---
title: "P8105_hw5_yw4200"
author: "yh"
date: "2023-11-04"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem 1

The Washington Post has gathered data on homicides in 50 large U.S. cities and made the data available through a GitHub repository here. You can read their accompanying article here.

Describe the raw data. Create a city_state variable (e.g. “Baltimore, MD”) and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).
```{r}
library(dplyr)
# import and summarize dataset
homicide <- read.csv("./local_data/homicide-data.csv")
summary(homicide)

# create a city_state variable
# I found that Tulsa corresponds to two states in the dataset, so delete the wrong one.
homicide_add <- homicide |>
  filter(!(city == "Tulsa" & state == "AL")) |>
  mutate(city_state = paste(city, state, sep = ", ")) 
head(homicide_add)

# compute the number of homicides within cities
homicide_city <- homicide_add |>
  group_by(city) |>
  summarise(
    total_homicides = n(), 
    unsolved_homicides = sum(disposition %in% c("Closed without arrest", "Open/No arrest"))
    )

homicide_city
```
Description of the raw data:

Over the course of the last ten years, The Washington Post gathered information on over 52,000 criminal homicides in 50 of the biggest American cities. The location of the murder, whether an arrest was made, and, for the most part, the basic demographics of each victim were among the data. The raw data includes `r length(names(homicide))` key variables, such as `r names(homicide)`. And the data has `r nrow(homicide)` observations.There are missing values in `lat` and `lon` columns and "unknown" values in `victim_race`, `victim_age`, `victim_sex`, `victim_last`, `victim_first`.

For the city of Baltimore, MD, use the prop.test function to estimate the proportion of homicides that are unsolved; save the output of prop.test as an R object, apply the broom::tidy to this object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe.

```{r}
library(broom)
# filter the dataset
balt_data <- homicide_add |>
  filter(city_state == "Baltimore, MD")

# use the prop.test to estimate the proportion of homicides that are unsolved
proptest_result <-
  prop.test(
    sum(balt_data$disposition %in% c("Closed without arrest", "Open/No arrest")),
    length(balt_data$disposition),
    conf.level = 0.95
)

tidy_result <- tidy(proptest_result)


# pull the estimated proportion and confidence intervals
paste("estimated proportion =", pull(tidy_result,estimate))
paste("confidence intervals =", "[", pull(tidy_result, conf.low), pull(tidy_result, conf.high), "]")
```

Now run prop.test for each of the cities in your dataset, and extract both the proportion of unsolved homicides and the confidence interval for each. Do this within a “tidy” pipeline, making use of purrr::map, purrr::map2, list columns and unnest as necessary to create a tidy dataframe with estimated proportions and CIs for each city.
```{r}
library(purrr)
library(tidyr)
# create a prop.test function for cities
proptest_city <- function(city,data) {
  proptest_result <- prop.test(
    sum(data$disposition %in% c("Closed without arrest", "Open/No arrest")),
    length(data$disposition),
    conf.level = 0.95
  )
  tidy_result <- tidy(proptest_result)
  tidy_result$city <- city
  return(tidy_result)
}

# nest the information except city and state
homicide_nest <- homicide_add |>
  select(city,everything()) |> 
  nest(others = uid:disposition)

# use map2 function to prop.test each city
results_list <- map2(
  homicide_nest$city,
  homicide_nest$others,
  ~proptest_city(.x, .y)
)

combined_results <- map_dfr(results_list, bind_rows) 

# create a tidy dataframe with estimated proportions and CIs
combined_results |> 
  select(city,estimate,conf.low,conf.high) |>
  mutate(CIs = paste0("[",conf.low,",",conf.high, "]"))

```
Create a plot that shows the estimates and CIs for each city – check out geom_errorbar for a way to add error bars based on the upper and lower limits. Organize cities according to the proportion of unsolved homicides.

```{r}
# Create a plot that shows the estimates and CIs for each city
library(ggplot2)

ggplot(combined_results, aes(group = city, y = reorder(city, estimate))) +
  geom_point(aes(x = estimate), size = 2) +
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high)) +
  labs(title = "Estimated proportion of unsolved homicides for each city",
       x = "Estimated Proportion",
       y = "City") +
  theme_light()
```

## Problem 2

This zip file contains data from a longitudinal study that included a control arm and an experimental arm. Data for each participant is included in a separate file, and file names include the subject ID and arm.

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:

Start with a dataframe containing all file names; the list.files function will help

Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe

Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary

```{r}
library(readr)
# import data use function
import_data = function(x) {
  read_csv(x) |>
  mutate(filename = x)
}

conexp_list = list.files("./local_data/problem2_data", pattern = "\\.csv$", full.names = T)

conexp_df = map(conexp_list, import_data)
conexp_data = bind_rows(conexp_df)
summary(conexp_data)
```

```{r}
# tidy the data and make it readable
conexp_clean <- conexp_data |>
  mutate(
    subject_id = substr(conexp_list, 32, 33),
    group = substr(conexp_list, 28, 30),
    ) |>
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    names_prefix = "week_",
    values_to = "observations"
  ) |>
  mutate(week = as.numeric(week)) |>
  select(subject_id,group,everything(),-filename)

head(conexp_clean)
```

Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.
```{r}
# make a spaghetti plot
conexp_plot <- conexp_clean |>
  ggplot(aes(x = week, y = observations, color = subject_id, group = subject_id)) +
  geom_line() +
  geom_point() +
  facet_grid(~ group) +
  labs(title = "Observations on each subject over time",
       x = "Week",
       y = "Observations") +
  theme_minimal()

conexp_plot
```
Comments:

The experimental group's subjects have higher observations over time than the control group's subjects. The observations of experimental group has an increasing trend as the week goes on, while the observations of control group stay stable as the week goes on.


Problem 3
When designing an experiment or analysis, a common question is whether it is likely that a true effect will be detected – put differently, whether a false null hypothesis will be rejected. The probability that a false null hypothesis is rejected is referred to as power, and it depends on several factors, including: the sample size; the effect size; and the error variance. In this problem, you will conduct a simulation to explore power in a one-sample t-test.

First set the following design elements:

Fix n=30

Fix σ=5

Set μ=0

Generate 5000 datasets from the model x∼Normal[μ,σ]

For each dataset, save μ̂ and the p-value arising from a test of H:μ=0, using α=0.05. Hint: to obtain the estimate and p-value, use broom::tidy to clean the output of t.test.
```{r}
# define a function to compute t.test
t_test = function(n = 30, mu = 0, sigma = 5) {
  
  test_data = tibble(
    x = rnorm(n, mean = mu, sd = sigma),
  )
  
  broom::tidy(t.test(test_data, mu = mu, alternative = "two.sided",conf.level = 0.95))
 
}

# Generate 5000 datasets
results_df = 
  expand_grid(
    sample_size = 30,
    iter = 1:5000
  ) |> 
  mutate(
    estimate_df = map(sample_size, t_test)
  ) |> 
  unnest(estimate_df)

# print the result
results_df |>
  select(estimate, p.value)

results_df1 <- results_df |>
  mutate(true_mu = 0)
```
Repeat the above for μ={1,2,3,4,5,6}, and complete the following:
```{r}
# create a new function related to mu
t_test2 = function(mu, sigma = 5) {
  sim_data <- tibble(
    x = rnorm(30, mean = mu, sd = sigma)
    )
  broom::tidy(t.test(sim_data))

}

results_df2 = 
  expand_grid(
    true_mu = c(1,2,3,4,5,6),
    iter = 1:5000
  ) |> 
  mutate(
    estimate_df = map(true_mu, t_test2)
  ) |> 
  unnest(estimate_df) 

result_combine = bind_rows(results_df1,results_df2)

head(result_combine)
```
Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of μ on the x axis. Describe the association between effect size and power.
```{r}
reject_plot <- result_combine |>
  group_by(true_mu) |>
  summarize(estimate = mean(estimate), power = mean(p.value < 0.05)) |>
  ggplot(aes(x = true_mu,y = power)) +
  geom_point() +
  geom_line() +
  scale_x_continuous(breaks = seq(0,6)) +
  labs(x = "True Mu",y = "Power of the Test",title = "Proportion of times the null was rejected") +
  theme_minimal()

reject_plot
```
Description:

It is expected that the power of the test will increase in association with the effect size, which is the difference between the true μ and the null hypothesis value. In other words, a larger effect means that the test can detect it more accurately.

Make a plot showing the average estimate of μ̂ on the y axis and the true value of μ on the x axis. Make a second plot (or overlay on the first) the average estimate of μ̂ only in samples for which the null was rejected on the y axis and the true value of μ on the x axis. Is the sample average of μ̂ across tests for which the null is rejected approximately equal to the true value of μ? Why or why not?

```{r}
# a plot showing the average estimate and the true value of mu
estimate_mu = result_combine |>
  group_by(true_mu) |>
  summarise(avg_estimate = mean(estimate))

mu_plot <- estimate_mu |>
  ggplot(aes(x = true_mu, y = avg_estimate)) +
  geom_point() +
  geom_line() +
  labs(x = "True Mu",y = "Average Estimate Mu",title = "Average estimate and true value of mu") +
  scale_x_continuous(breaks = seq(0,6)) + 
  scale_y_continuous(breaks = seq(0,6)) + 
  theme_minimal()

mu_plot
```

```{r}
# a second plot for the average estimate of mu which the null was rejected and the true value of mu
reject_mu = result_combine |>
  filter(p.value < 0.05) |>
  group_by(true_mu) |>
  summarise(avg_estimate = mean(estimate))

reject_mu_plot <- reject_mu |>
  ggplot(aes(x = true_mu, y = avg_estimate)) +
  geom_point() +
  geom_line() +
  labs(x = "True Mu",y = "Average Estimate Mu",title = "Average estimate(which the null was rejected) and true value of mu") +
  scale_x_continuous(breaks = seq(0,6)) + 
  scale_y_continuous(breaks = seq(0,6)) + 
  theme_minimal()

reject_mu_plot

```
The sample average of mu across tests for which the null is rejected approximately equal to the true value of mu.

The average estimate means of whose null are rejected differ from the true mean when the true mean is small(1-3). This could be as a result of the low power at low effect size. The average estimate means of whose null are rejected are similar to the true mean when the true mean is greater than 3.The samples were randomly selected from the distribution x∼Normal[μ,σ]. When the number of samples is large enough and null rejected samples, their mean distribution tends to be approximately symmetric to the true μ due to the randomness.


